\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage{amsfonts, amsmath, amssymb}

% this should be the last package used
\usepackage{pdfsetup}

% urls in roman style, theory text in math-similar italics
\urlstyle{rm}
\isabellestyle{it}


\begin{document}

\title{Auto2 prover}
\author{Bohua Zhan}
\maketitle

\begin{abstract}
  Auto2 is a saturation-based heuristic prover for higher-order logic,
  implemented as a tactic in Isabelle.

  This entry contains the instantiation of auto2 for Isabelle/HOL,
  along with several examples. This includes: solutions to some of the
  Pelletier's problems, elementary number theory of primes, functional
  algorithms and data structures, and verification of imperative
  programs using separation logic.
\end{abstract}

\newpage
\tableofcontents
\newpage
\parindent 0pt\parskip 0.5ex

\section{Introduction}

Auto2 \cite{zhan16} is a proof automation tool implemented in
Isabelle. It uses a saturation-based approach to proof search:
starting with a list of initial assumptions, it iteratively adds facts
that can be derived from these assumptions, with the aim of ultimately
deriving a contradiction. Users can add their own proof procedures to
auto2 in the form of \emph{proof steps}, in order to implement
domain-specific knowledge. Auto2 can be instantiated to both
Isabelle/HOL (for ordinary usage) and Isabelle/FOL (for formalization
of mathematics based on set theory).

This AFP entry contains the instantiation of auto2 to Isabelle/HOL,
and several sample applications:

\begin{itemize}
\item Pelletier's problems: solutions to some of the problems in
  Pelletier's collection of problems for testing automatic theorem
  provers \cite{pelletier}. Auto2 is not intended to compete with
  ATPs. In our examples, we merely show how to use the prover to solve
  some of the problems, sometimes with hints.

\item Elementary number theory: theory of prime numbers up to the
  infinitude of primes and unique factorization. This example follows
  the development in HOL/Computational\_Algebra/Primes.thy in the
  Isabelle distribution.

\item Functional programs: we verify several functional algorithms and
  data structures, including: linked lists, binary search trees,
  red-black trees, interval trees, priority queue, quicksort,
  union-find, Dijkstra's algorithm, and a sweep-line algorithm for
  detecting rectangle intersection.

\item Imperative programs: we verify imperative versions of the above
  algorithms and data structures, using Isabelle's Imperative HOL
  framework \cite{imphol}. We make use of separation logic, following
  the framework set up by Lammich and Reis \cite{seplogic-afp}. The
  general outline of some of the examples also come from there. The
  program verification examples are described in \cite{zhan18a}.
\end{itemize}

\input{session}

\bibliographystyle{abbrv}
\bibliography{root}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
